Are environmental and geographic variables effective surrogates for genetic variation in conservation planning?

### 2016-05-11 code/rmarkdown/article.Rmd
+ fix for stats in article
Former-commit-id: ca2b26947e16991e13f5023b668df5178cf80b76

<!-- scenario analysis -->
To determine if the addition of environmental and geographic targets could improve the effectiveness of prioritizations in a more realistic context, we generated prioritizations according to three scenarios using different combinations of targets (Figure 3). We then computed the proportion of adaptive and neutral genetic variation secured in each prioritization (Figure 4). The proportion of genetic variation secured in a prioritization was found to depend on the combination of targets used to generate the prioritization (${\chi^2}_{`r scenario.ANOVA.4.DF$Chi.Df[[2]]`} = `r round(scenario.ANOVA.4.DF$statistic[[2]],2)`$; $P `r pvalString(scenario.ANOVA.4.DF$Pr..Chisq.[[2]])`)$. Specifically, the amount-based prioritizations tended to secure less variation than the prioritizations generated using additional surrogate ($Z_1 = `r round(scenario.GLHT.2.DF$statistic[[1]],2)`$; $P `r pvalString(scenario.GLHT.2.DF$p.value[[1]])`$) or genetic variables ($Z_1 = `r round(scenario.GLHT.2.DF$statistic[[2]],2)`$; $P `r pvalString(scenario.GLHT.2.DF$p.value[[2]])`$). No evidence was found to suggest that the prioritizations that included additional surrogate- or genetic-based targets secured a different proportion of genetic variation ($Z_1 = `r round(scenario.GLHT.2.DF$statistic[[3]],2)`$; $P = `r pvalString(scenario.GLHT.2.DF$p.value[[3]])`$). We also found that the prioritizations tended to secure more adaptive than neutral genetic variation (${\chi^2}_{`r scenario.ANOVA.3.DF$Chi.Df[[2]]`} = `r round(scenario.ANOVA.3.DF$statistic[[2]],2)`$; $P `r pvalString(scenario.ANOVA.3.DF$Pr..Chisq.[[2]])`$). We also found significant differences in the average proportion of genetic variation secured by prioritizations in each of the scenarios (${\chi^2}_{`r scenario.ANOVA.2.DF$Chi.Df[[2]]`} = `r round(scenario.ANOVA.2.DF$statistic[[2]],2)`$; $P$ `r pvalString(scenario.ANOVA.2.DF$Pr..Chisq.[[2]])`). Specifically, both the multi-species ($Z_1 = `r round(scenario.GLHT.1.DF$statistic[[1]],2)`$; $P = `r pvalString(scenario.GLHT.1.DF$p.value[[1]])`$) and multi-species with cost ($Z_1 = `r round(scenario.GLHT.1.DF$statistic[[2]],2)`$; $P `r pvalString(scenario.GLHT.1.DF$p.value[[2]])`$) scenarios were found to secure more genetic variation than the single species scenario. Neither the multi-species scenarios were found to secure a different proportion of genetic variation ($Z_1 = `r round(scenario.GLHT.1.DF$statistic[[3]],2)`$; $P `r pvalString(scenario.GLHT.1.DF$p.value[[3]])`$). These results suggest that surrogate-based targets can substantially improve the proportion of intra-specific genetic variation secured in a prioritization for most species.

## Discussion
* introduction

@@

* outlier detection methods - how does our findings agree with other papers?

* mapping genetic variation - compare with GDMS

>>>>

<!-- scenario analysis -->
To determine if the addition of environmental and geographic targets could improve the effectiveness of prioritizations in a more realistic context, we generated prioritizations according to three scenarios using different combinations of targets (Figure 3). We then computed the proportion of adaptive and neutral genetic variation secured in each prioritization (Figure 4). The proportion of genetic variation secured in a prioritization was found to depend on the combination of targets used to generate the prioritization (${\chi^2}_{`r scenario.ANOVA.4.DF$Chi.Df[[2]]`} = `r round(scenario.ANOVA.4.DF$statistic[[2]],2)`$; $P `r pvalString(scenario.ANOVA.4.DF$Pr..Chisq.[[2]])`)$. Specifically, the amount-based prioritizations tended to secure less variation than the prioritizations generated using additional surrogate (`r round(plogis(scenario.GLHT.2.DF$estimate[[1]])*100,2)` % mean difference $\pm$ `r round(plogis(scenario.GLHT.2.DF$std.error[[1]])*100,2)` SE ; $Z_1 = `r round(scenario.GLHT.2.DF$statistic[[1]],2)`$; $P `r pvalString(scenario.GLHT.2.DF$p.value[[1]])`$) or genetic variables (`r round(plogis(scenario.GLHT.2.DF$estimate[[2]])*100,2)` % mean difference $\pm$ `r round(plogis(scenario.GLHT.2.DF$std.error[[2]])*100,2)` SE; `$Z_1 = `r round(scenario.GLHT.2.DF$statistic[[2]],2)`$; $P `r pvalString(scenario.GLHT.2.DF$p.value[[2]])`$). No evidence was found to suggest that the prioritizations that included additional surrogate- or genetic-based targets secured a different proportion of genetic variation (`r round(plogis(scenario.GLHT.2.DF$statistic[[3]])*100,2)` % mean difference $\pm$ `r round(plogis(scenario.GLHT.2.DF$std.error[[3]])*100,2)` SE; $Z_1 = `r round(scenario.GLHT.2.DF$statistic[[3]],2)`$; $P = `r pvalString(scenario.GLHT.2.DF$p.value[[3]])`$). We also found that the prioritizations tended to secure more adaptive than neutral genetic variation (`r round(plogis(scenario.GLHT.3.DF$statistic[[1]])*100,2)` % mean difference $\pm$ `r round(plogis(scenario.GLHT.3.DF$std.error[[1]])*100,2)` SE; ${\chi^2}_{`r scenario.ANOVA.3.DF$Chi.Df[[2]]`} = `r round(scenario.ANOVA.3.DF$statistic[[2]],2)`$; $P `r pvalString(scenario.ANOVA.3.DF$Pr..Chisq.[[2]])`$). We also found significant differences in the average proportion of genetic variation secured by prioritizations in each of the scenarios (${\chi^2}_{`r scenario.ANOVA.2.DF$Chi.Df[[2]]`} = `r round(scenario.ANOVA.2.DF$statistic[[2]],2)`$; $P$ `r pvalString(scenario.ANOVA.2.DF$Pr..Chisq.[[2]])`). Specifically, both the multi-species (`r round(plogis(scenario.GLHT.1.DF$estimate[[1]])*100,2)` % mean difference $\pm$ `r round(plogis(scenario.GLHT.1.DF$std.error[[1]])*100,2)` SE; $Z_1 = `r round(scenario.GLHT.1.DF$statistic[[1]],2)`$; $P = `r pvalString(scenario.GLHT.1.DF$p.value[[1]])`$) and multi-species with cost (`r round(plogis(scenario.GLHT.1.DF$estimate[[2]])*100,2)` % mean difference $\pm$ `r round(plogis(scenario.GLHT.1.DF$std.error[[2]])*100,2)` SE; $Z_1 = `r round(scenario.GLHT.1.DF$statistic[[2]],2)`$; $P `r pvalString(scenario.GLHT.1.DF$p.value[[2]])`$) scenarios were found to secure more genetic variation than the single species scenario. Neither the multi-species scenarios were found to secure a different proportion of genetic variation (`r round(plogis(scenario.GLHT.1.DF$estimate[[3]])*100,2)` % mean difference $\pm$ `r round(plogis(scenario.GLHT.1.DF$std.error[[3]])*100,2)` SE; $Z_1 = `r round(scenario.GLHT.1.DF$statistic[[3]],2)`$; $P `r pvalString(scenario.GLHT.1.DF$p.value[[3]])`$). These results suggest that surrogate-based targets can substantially improve the proportion of intra-specific genetic variation secured in a prioritization for most species.

## Discussion
* introduction
We aimed  to investigate the effectiveness of broad-scale environmental and geographic variables as surrogates for adaptive and neutral genetic variation in conservation planning. Our study is the first to address this hypothesis using moderately realistic planning scenarios. Overall, we found that the spatial patterns of environmental and geographic variables correlate with those of adaptive and neutral patterns for most species. Furthermore, we found that the addition of environmental and geographic targets to the planning process resulted in prioritizations that generally secured a greater proportion of adaptive and neutral genetic variation.

@@

* outlier detection methods

* mapping genetic variation
